\Large \bf Dark Decoys: Conjuring Proxies from Unused Address Space

### 2019-02-15 paper/paper.tex
Revise first half intro

% to be able to draw some self-contained figs
\usepackage{tikz}
%\usepackage{parskip}
\usepackage{mathptmx}\renewcommand{\ttdefault}{cmtt}
\usepackage{amsmath}
\usepackage{wasysym}
%\setlength{\parskip}{1pt} % 1ex plus 0.5ex minus 0.2ex}
%\setlength\parskip{1pt}
\usepackage{graphicx} % http://ctan.org/pkg/graphicx
\usepackage{booktabs} % http://ctan.org/pkg/booktabs
\usepackage{xparse}   % http://ctan.org/pkg/xparse%don't print date
\NewDocumentCommand{\rot}{O{45} O{1em} m}{\makebox[#2][l]{\rotatebox{#1}{#3}}}%
\include{figures}
\usepackage{subcaption}
\usepackage{cleveref}
\usepackage{microtype}
\SetExtraKerning{encoding=*,font=*}{\textemdash={120,120}} % Add space around emdashes
\usepackage[font=small]{caption}
\microtypecontext{spacing=nonfrench}
\usepackage{subcaption}
\usepackage{xspace}
\usepackage{soul}
\newcommand{\note}[2]{\hl{[\textbf{#1:} #2]}\xspace}
\newcommand{\nikita}[1]{\note{nikita}{#1}}

@@

%\newcommand{\scheme}{Conjure\xspace}
\newcommand{\scheme}{Dark Decoys\xspace}

%-------------------------------------------------------------------------------
\begin{abstract}
%-------------------------------------------------------------------------------
Refraction Networking (formerly known as ``Decoy Routing'') has
emerged as a promising next-generation approach for circumventing
Internet censorship. Rather than trying to hide individual
circumvention proxy servers from censors, proxy functionality is
implemented in the core of the network, at cooperating ISPs in
friendly countries.  Any connection that traverses these ISPs could be
a conduit for the free flow of information, so censors cannot easily
block access without also blocking many legitimate sites.  While one
Refraction scheme, TapDance, has recently been deployed at ISP-scale,
it suffers from several problems: a limited number of ``decoy'' sites
in realistic deployments, high technical complexity, and undesirable
tradeoffs between performance and observability by the censor. These
problems may impede broader deployment and ultimately allow censors to
block such techniques.

@@

%Censorship circumvention still important
%-More countries blocking
%-Existing countries blocking more
Internet censorship continues to hamper social progress throughout the world.
Over half of the global Internet population
now live in countries that block political, social, or religious content
online~\cite{fotn2018} as governments continue to expand their censorship
policies and programs.

%Existing circumvention strategies on shaky ground
%-domain fronting going away
%-active probing of existing proxies
%-Cenosrs fingerprinting known protocols
Meanwhile, strategies to circumvent censorship using proxies have suffered many
recent setbacks. Many previously popular proxies are no longer functional due to
censors evolving new ways to block them~\cite{ensafi-tor,great-cannon},
or because they rely on temperamental
infrastructure. For example, domain fronting was a popular circumvention
strategy used by meek (in Tor), as well as the Signal secure messaging app to
get around censorship in countries it was
blocked~\cite{meek,signal,signal-domain-fronting}.
But in May~2018, Google and Amazon made both technical and policy changes to
their cloud infrastructures that removed support for domain
fronting~\cite{aws-front}. While meek
continues to use other cloud providers that (for now) continue to allow domain
fronting, Signal abandoned the strategy altogether~\cite{signal-back-on-front}.
%Combined with censors' constant improvements in discovery and blocking
%techniques~\cite{ensafi-tor,great-cannon}, ...

%Importance of Refraction Networking
%-what it is, how it solves many of the above problems
%-acknowledge challenge of ISP deployment, cite TapDance deployment as only refraction technology that has overcome this challenge so far
One emerging technique is Refraction Networking (also known as ``Decoy
Routing''), which places proxies at cooperating Internet Service Providers
(ISPs) outside censoring countries~\cite{refraction-site}. Clients access the
proxies by connecting to unblocked ``decoy'' sites such that the packets pass by
the ISP proxy, which intercepts and injects responses as the decoy site.
Censors cannot easily block access without also blocking
legitimate connections to the decoy sites, which may be costly for the censor.
However, deploying such schemes in practice is more difficult than existing proxies:
convincing ISPs to deploy proxies in their production network is a significant
operational hurdle. To date, only one of six Refraction
Networking schemes has been deployed in practice by a large ISP:
TapDance~\cite{tadance14}, a
Refraction Networking protocol that removes the need for inline
flow-blocking~\cite{frolov2017isp}.

@@

%Dark decoys solve these issues
%-Create new decoys from ``dark'' (unused) address space
%-Clients register (via TapDance-like or other robust protocol (email, blockchain, whatever))
%-Connect to custom IP address, talk whatever protocol client/station agrees on
In this paper, we present Dark Decoys, a new Refraction Networking protocol that
solves these issues, while maintaining the easy-to-deploy model of TapDance
(i.e. a passive network tap). In our scheme, clients register new fictitious
decoys in the ``dark'' or unused address space of the deploying ISP. Once
registered, clients can connect to these dark decoy IP addresses as if they were
real hosts. The ISP station acts as the other end of these connections, and responds as
if it were a legitimate site or service. To the censor, these dark decoys appear
as legitimate sites or services, and even active probes won't reveal
information that would allow the censor to block them.

@@

We implemented the Dark Decoy protocol and tested it in a 10~Gbps ISP testbed
with real traffic. Similar to TapDance~\cite{tapdance}, we used PF\_RING to
consume the 10~Gbps link, and feed it to a custom \textbf{detector} written in Rust. The
detector processes all packets and watches for new registrations. It also
forwards all packets sent to a (registered) dark decoy's address to the local
\textbf{application} via an \texttt{iptables} DNAT rule that rewrites the destination IP,
allowing the application to accept and respond to connections using the native
operating system's interface. Figure~\ref{fig:implementation} shows the overall
architecture of our implementation, which we describe next.
% Along with the client?

@@

Client begins registation by establishing TLS connection
to one of the reachable websites,
path to which passes by our tap.
Client uses a Chosen-Ciphertext Steganography technique~\cite{tapdance} to manupulate
plaintext of a first application data HTTP request
to get desired ciphertext,
and exchange keys with the station.
After client writes Elligator-encoded~\cite{elligator} representative into the ciphertext at a static offset of 92 bytes from the end,
that could be decoded using station's private key,
to negotiate a 32 byte Eligator-encoded~\cite{elligator} shared secret between the client and the station.
That shared secret is used as a seed of SHA-256 based key derivation function (HKDF),
allowing station and client to derive an unlimited amount of shared secrets.

@@

@@

Rebound~\cite{rebound15} and Waterfall~\cite{waterfall} both focus on routing
asymmetries and routing attacks by the censor. Rebound modifies the client's
packets on the way to the decoy, and uses error pages on the decoy site to
reflect data back to the client. Waterfall only observes and modifies the
decoy-to-client traffic, similarly using error pages on the decoy to reflect
communication from the client to the station. These schemes also provide some
resistance to traffic analysis, as they use the real decoy to reflect data to
the user. Thus, the TCP/TLS behavior seen by the censor more closely matches
that of a legitimate decoy connection. However, latency and other packet-timing
characteristics may be observable, and both schemes require some form of inline
flow blocking.

@@

@@

@@

>>>>

% to be able to draw some self-contained figs
\usepackage{tikz}
%\usepackage{parskip}
\usepackage{mathptmx}\renewcommand{\ttdefault}{cmtt}
\usepackage{amsmath}
\usepackage{wasysym}
%\setlength{\parskip}{1pt} % 1ex plus 0.5ex minus 0.2ex}
%\setlength\parskip{1pt}
\usepackage{graphicx} % http://ctan.org/pkg/graphicx
\usepackage{booktabs} % http://ctan.org/pkg/booktabs
\usepackage{xparse}   % http://ctan.org/pkg/xparse%don't print date
\NewDocumentCommand{\rot}{O{45} O{1em} m}{\makebox[#2][l]{\rotatebox{#1}{#3}}}%
\include{figures}
\usepackage{subcaption}
\usepackage{cleveref}
\usepackage{microtype}
\SetExtraKerning{encoding=*,font=*}{\textemdash={120,120}} % Add space around emdashes
\usepackage[font=small]{caption}
\microtypecontext{spacing=nonfrench}
\usepackage{subcaption}
\usepackage{xspace}
\usepackage{soul}
\newcommand{\note}[2]{\hl{[\textbf{#1:} #2]}\xspace}
\newcommand{\nikita}[1]{\note{nikita}{#1}}
\newcommand{\TODO}[1]{\hl{TODO: #1}\xspace}
\newcommand{\TK}{\hl{TK}\xspace}

@@

\newcommand{\scheme}{Conjure\xspace}
%\newcommand{\scheme}{Dark Decoys\xspace}

%-------------------------------------------------------------------------------
\begin{abstract}
%-------------------------------------------------------------------------------
Refraction Networking (formerly known as ``Decoy Routing'') has
emerged as a promising next-generation approach for circumventing
Internet censorship. Rather than trying to hide individual
circumvention proxy servers from censors, proxy functionality is
implemented in the core of the network, at cooperating ISPs in
friendly countries.  Any connection that traverses these ISPs could be
a conduit for the free flow of information, so censors cannot easily
block access without also blocking many legitimate sites.  While one
Refraction scheme, TapDance, has recently been deployed at ISP-scale,
it suffers from several problems: a limited number of ``decoy'' sites
in realistic deployments, high technical complexity, and undesirable
tradeoffs between performance and observability by the censor. These
challenges may impede broader deployment and ultimately allow censors to
block such techniques.

@@

%Censorship circumvention still important
%-More countries blocking
%-Existing countries blocking more
%Internet censorship continues to hamper social progress throughout the world.

Over half of Internet users globally
now live in countries that block political, social, or religious content
online~\cite{fotn2018}.
%Existing circumvention strategies on shaky ground
%-domain fronting going away
%-active probing of existing proxies
%-Cenosrs fingerprinting known protocols
Meanwhile, many popular tools and techniques for circumventing such censorship
have ceased to function, because censors have evolved new ways to block them~\cite{ensafi-tor,great-cannon}
or infrastructure they rely on has become unavailable.

For example, domain fronting~\cite{meek} was a popular circumvention
strategy used by Meek (in Tor), as well as by the Signal secure messaging app to
get around censorship in countries where it was
blocked~\cite{signal,signal-domain-fronting}.
But in May~2018, Google and Amazon made both technical and policy changes to
their cloud infrastructures that removed support for domain
fronting~\cite{aws-front}. While meek
continues to use other cloud providers that (for now) continue to allow domain
fronting, Signal abandoned the strategy altogether~\cite{signal-back-on-front}.
There is an urgent need for new, more robust approaches to circumvention.

%Combined with censors' constant improvements in discovery and blocking
%techniques~\cite{ensafi-tor,great-cannon}, ...

%Importance of Refraction Networking
%-what it is, how it solves many of the above problems
%-acknowledge challenge of ISP deployment, cite TapDance deployment as only refraction technology that has overcome this challenge so far
A family of techniques called Refraction Networking~\cite{refraction-site,telex11,cirripede11,curveball11,tapdance14,rebound15,slitheen16,waterfall17}, formerly known
as Decoy Routing, has made promising steps towards that goal.
These techniques operate in the network's core, at cooperating Internet Service Providers
(ISPs) outside censoring countries.  Clients access circumvention service by connecting to a ``decoy site''---any uncensored website for which the connection travels over a participating ISP\@.  Upon recognizing a steganographic signal from the client, the ISP modifies the connection response to return censored content requested by the user.
Censors cannot easily block access without also blocking legitimate connections to the decoy sites---collateral damage that may be prohibitively costly for the censor~\cite{robinson2013collateral}.

However, deploying such schemes in practice is more difficult than existing proxies:
convincing ISPs to deploy proxies in their production network is a significant
operational hurdle. To date, only one of six Refraction
Networking schemes has been deployed in practice by a large ISP:
TapDance~\cite{tapdance14}, a
Refraction Networking protocol that removes the need for inline
flow-blocking~\cite{frolov2017isp}.

@@

%Dark decoys solve these issues
%-Create new decoys from ``dark'' (unused) address space
%-Clients register (via TapDance-like or other robust protocol (email, blockchain, whatever))
%-Connect to custom IP address, talk whatever protocol client/station agrees on
In this paper, we present \scheme, a new Refraction Networking protocol that
solves these issues, while maintaining the easy-to-deploy model of TapDance
(i.e. a passive network tap). In our scheme, clients register new fictitious
decoys in the ``dark'' or unused address space of the deploying ISP. Once
registered, clients can connect to these dark decoy IP addresses as if they were
real hosts. The ISP station acts as the other end of these connections, and responds as
if it were a legitimate site or service. To the censor, these phantom hosts appear
as legitimate sites or services, and even active probes won't reveal
information that would allow the censor to block them.

@@

We implemented the Dark Decoy protocol and tested it in a 10~Gbps ISP testbed
with real traffic. Similar to TapDance~\cite{tapdance14}, we used PF\_RING to
consume the 10~Gbps link, and feed it to a custom \textbf{detector} written in Rust. The
detector processes all packets and watches for new registrations. It also
forwards all packets sent to a (registered) dark decoy's address to the local
\textbf{application} via an \texttt{iptables} DNAT rule that rewrites the destination IP,
allowing the application to accept and respond to connections using the native
operating system's interface. Figure~\ref{fig:implementation} shows the overall
architecture of our implementation, which we describe next.
% Along with the client?

@@

Client begins registation by establishing TLS connection
to one of the reachable websites,
path to which passes by our tap.
Client uses a Chosen-Ciphertext Steganography technique~\cite{tapdance14} to manupulate
plaintext of a first application data HTTP request
to get desired ciphertext,
and exchange keys with the station.
After client writes Elligator-encoded~\cite{elligator} representative into the ciphertext at a static offset of 92 bytes from the end,
that could be decoded using station's private key,
to negotiate a 32 byte Eligator-encoded~\cite{elligator} shared secret between the client and the station.
That shared secret is used as a seed of SHA-256 based key derivation function (HKDF),
allowing station and client to derive an unlimited amount of shared secrets.

@@

\TODO{Write (1 page)}

@@

Rebound~\cite{rebound15} and Waterfall~\cite{waterfall17} both focus on routing
asymmetries and routing attacks by the censor. Rebound modifies the client's
packets on the way to the decoy, and uses error pages on the decoy site to
reflect data back to the client. Waterfall only observes and modifies the
decoy-to-client traffic, similarly using error pages on the decoy to reflect
communication from the client to the station. These schemes also provide some
resistance to traffic analysis, as they use the real decoy to reflect data to
the user. Thus, the TCP/TLS behavior seen by the censor more closely matches
that of a legitimate decoy connection. However, latency and other packet-timing
characteristics may be observable, and both schemes require some form of inline
flow blocking.

@@

\TODO{Write (0.5--0.75 page)}

@@

\TODO{Write (0.5 page)}

@@

\TODO{Write (0.25 page}
